### 2015-05-06 conclusion.tex
Daily update: conclusion

\citet{Xenakis20063225}

@@

\paragraph{Cryptographic libraries}
OpenSSL is not the only cryptographic library available; PolarSSL and GnuTLS could also be viable solutions.
%TODO see if they can use cryptodev, that would be perfect.

>>>>

@@

\paragraph{Cryptographic libraries}
OpenSSL is not the only cryptographic library available; GnuTLS is also a very popular alternative and supports cryptodev engines too.

However, one library definitely worth to keep an eye on is mbed TLS, formally known as PolarSSL, recently bought by ARM~\cite{2015-arm-buy-polarssl}.
We can expect the future releases of this library to be more optimized for ARM platforms, and maybe the software footprint and overhead to be reduced.
